Supplementary material

### 2021-06-30 submission/supplement.rmd
fix typo; closes #1
rebuild supplement

---
title: "Supplementary material"
output:
    bookdown::pdf_document2: default
geometry: margin=1.0in
toc: false
font-size: 12pt
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \newcommand\given[1][]{\:#1\vert\:}
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: jce.csl
---

>>>>

---
title: "Supplementary material"
output:
    bookdown::pdf_document2: default
geometry: margin=1.0in
toc: false
font-size: 12pt
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \newcommand\given[1][]{\:#1\vert\:}
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: jce.csl
---
